### 2015-11-04 figures/Figure2-flowDiagram.tex
Added --ignore option. Iterated results.

% Flowchart
% Author: Qrrbrbirlbel
\documentclass[tikz,border=10pt]{standalone}
%%%<
\usepackage{verbatim}
%%%>
\begin{comment}
:Title: Flowchart
:Tags: Diagrams;Flowcharts;Node positioning;Nodes and shapes
:Author: Qrrbrbirlbel
:Slug: flowchart

This example flowchart uses the positioning-plus library and the
node-families library by the same author. The fit library is implicitly loaded
by positioning-plus, the backgrounds library is used to draw stuff behind
other stuff, the calc library for some coordinate calculations and the
shapes.geometric library for the ellipse shape.

This example was written by Qrrbrbirlbel answering a question on TeX.SE.
\end{comment}
\usetikzlibrary{shapes.geometric,backgrounds,
  positioning-plus,node-families,calc}
\tikzset{
  basic box/.style = {
    shape = rectangle,
    align = center,
    draw  = #1,
    fill  = #1!25,
    rounded corners},
  header node/.style = {
    Minimum Width = header nodes,
    font          = \strut\Large\ttfamily,
    text depth    = +0pt,
    fill          = white,
    draw},
  header/.style = {%
    inner ysep = +1.5em,
    append after command = {
      \pgfextra{\let\TikZlastnode\tikzlastnode}
      node [header node] (header-\TikZlastnode) at (\TikZlastnode.north) {#1}
      node [span = (\TikZlastnode)(header-\TikZlastnode)]
        at (fit bounding box) (h-\TikZlastnode) {}
    }
  },
  hv/.style = {to path = {-|(\tikztotarget)\tikztonodes}},
  vh/.style = {to path = {|-(\tikztotarget)\tikztonodes}},
  fat blue line/.style = {ultra thick, blue}
}
\begin{document}
\begin{tikzpicture}[node distance = 1.2cm, thick, nodes = {align = center},
    >=latex]
  \node[Minimum Width = loop, shape = ellipse, fill = red] (imp-sol)
    {ellipsoid box};
  \node[Minimum Width = loop, fill = yellow, below = of imp-sol] (rec-box)
    {rectangular box, and very wiiiiiiiiiiiiiiide\\2nd line};
  \node[shift = (left:.5*x_node_dist)] at
    ($(imp-sol.west|-imp-sol.south)!.5!(rec-box.north west)$) (for-1)
    {formula 1};
  \node[shift = (right:.5*x_node_dist)] at
    ($(imp-sol.east|-imp-sol.south)!.5!(rec-box.north east)$) (for-2)
    {formula 2};
  \begin{scope}[on background layer]
    \node[fit = (for-1)(for-2)(imp-sol)(rec-box), basic box = blue,
      header = DMFT loop] (dmft-l) {};
  \end{scope}
  \path[very thick, blue, hv] (rec-box) edge[->] (for-1) edge[<-] (for-2)
                              (imp-sol) edge[->] (for-2) edge[<-] (for-1);

  \node[east above = of dmft-l, basic box = green, header = DMFT prelude]
    (dmft-p) {Math and text math and text math and text\\
              math and text math and text math and text};
  \node[north left = of dmft-l, basic box = green, header = $\rho$ update,
     shift = (down:y_node_dist)] (rho)
    {Much more text much more text\\much more text much more text};
  \node[basic box = blue, header = DFT part, anchor = north] at
    (dmft-p.north-|rho) (dft) {So much text so much text so much text\\
    I think I need \texttt{tikz-lipsum}\\or something like that.};
  \node[basic box = green, anchor = north] at
    ($(dft.north east)!.5!(dmft-p.north west)$) (upd) {update\\$math$};
  \path[fat blue line, <-, dashed, vh] (rho) edge
    ({$(rho.south)!.5!(dmft-l.south)$}-|dmft-l.south west);
  \path[fat blue line, ->]
    ({$(upd.south)!.5!(dmft-p.south)$}-|dmft-p.south west)
    coordinate (@) edge[<-, solid] coordinate[pos=.15] (@s)
    coordinate[pos=.9] (@e) (@-|dft.east)
    {[every edge/.append style=dashed, vh] (@s) edge[<-] (upd) (@e) edge (upd)}
    (h-rho) edge[dashed] (dft)
    ($(dmft-p.south)!.5!(dmft-p.south east)$)
    coordinate (@) edge (@|-dmft-l.north);
\end{tikzpicture}
\end{document}

>>>>

\documentclass{article}

\usepackage[latin1]{inputenc}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

%%%<
\usepackage{verbatim}
\usepackage[active,tightpage]{preview}
\PreviewEnvironment{tikzpicture}
\setlength\PreviewBorder{5pt}%
%%%>

\begin{comment}
:Title: Simple flow chart
:Tags: Diagrams

With PGF/TikZ you can draw flow charts with relative ease. This flow chart from [1]_
outlines an algorithm for identifying the parameters of an autonomous underwater vehicle model.

Note that relative node
placement has been used to avoid placing nodes explicitly. This feature was
introduced in PGF/TikZ >= 1.09.

.. [1] Bossley, K.; Brown, M. & Harris, C. Neurofuzzy identification of an autonomous underwater vehicle `International Journal of Systems Science`, 1999, 30, 901-913

\end{comment}

\begin{document}
% Define the layers to draw the diagram
\pgfdeclarelayer{background}
\pgfdeclarelayer{foreground}
\pgfsetlayers{background,main,foreground}
\pagestyle{empty}
\renewcommand{\arraystretch}{0.75}

%POSITIVE TERMS:
%egrep 'befit|winner|encourag|metric|noisy|algorithms$|kernel$|methods$|procedure$|programs$|software$|technologies$|accuracy$|analysis$|benchmark|comparing$|comparison$|comprehensive$|estimation$|evaluation$|effectiveness$|metrics$|efficiency$|performance$|perspective$|quality$|rated$|suitable$|suitability$|superior$|survey$|cputime$|speed$|time$|duration$|fast$|slow$' wordScores.tsv | sort -nr | egrep -v 'mrsfast|mrfast|alignmentmethods' | head -n 5  | perl -lane 'print "{\\tiny $F[0]} & {\\tiny $F[1]} & {\\tiny $F[2]} & {\\tiny $F[3]}\\\\"'

%NEGATIVE TERMS:
%egrep 'mirnas$|associated$|disease$|genes$|human$|proteins$|genetic$|pathways$|mrna$|cdna$|functional$|clinical$|regulation$|predicted$|interaction$|review$|network' 
%cat wordScores.tsv | sort -nr | egrep -v 'xxxxxx' | tail -n 5  | perl -lane 'print "{\\tiny $F[0]} & {\\tiny $F[1]} & {\\tiny $F[2]} & {\\tiny $F[3]}\\\\"'

% Define block styles
\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
    text width=5em, text centered, rounded corners, minimum height=4em]
\tikzstyle{line} = [draw, line width=1mm, -latex']
\tikzstyle{cloud} = [draw, rectangle,fill=red!20, 
       text width=14em, text centered, rounded corners, minimum height=4em]
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
    text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]

\begin{tikzpicture}[->,node distance = 6cm, auto,thick,main node/.style={font=\sffamily\Large\bfseries}]
    % Place nodes
    \node [align=center]                              (dummy)  {}; 
%    \node [block]                  (dummy)  {}; 
    \node [block, left of=dummy,   node distance=4.5cm] (init1)  {Training articles};
    \node [block, right of=dummy,  node distance=4.5cm] (init2)  {Background articles};
    \node [cloud, below of=dummy,  node distance=1cm] (remove) {Remove high freq. words};
    \node [cloud, below of=remove, node distance=2.5cm] (freqs)  {Compute word \& di-word freqs};
    \node [cloud, below of=freqs,  node distance=4cm] (lods)   {Compute word scores: $s(word)=\log_2\left(\frac{f_{training}(word)+\delta}{f_{background}(word)+\delta}\right)$\\
\begin{tabular}{llll}
{\tiny logOdds} & {\tiny tnFreq} & {\tiny bgFreq} & {\tiny word}\\
{\tiny 5.28}    & {\tiny 0.0019} & {\tiny 0.0000} & {\tiny benchmarking}\\
{\tiny 5.21}    & {\tiny 0.0061} & {\tiny 0.0002} & {\tiny benchmark}\\
{\tiny 4.91}    & {\tiny 0.0011} & {\tiny 0.0000} & {\tiny noisy}\\
{\tiny 4.85}    & {\tiny 0.0022} & {\tiny 0.0001} & {\tiny metrics}\\
{\tiny 4.85}    & {\tiny 0.0003} & {\tiny 0.0000} & {\tiny encouragingly}\\
...\\
{\tiny -7.90}   & {\tiny 0.0000} & {\tiny 0.0024} & {\tiny disease}\\
{\tiny -8.02}   & {\tiny 0.0000} & {\tiny 0.0026} & {\tiny associated}\\
{\tiny -8.09}   & {\tiny 0.0000} & {\tiny 0.0027} & {\tiny mirnas}\\
\end{tabular}
};
    \node [cloud, below of=lods, node distance=4cm]     (score)  {Score \& rank candidate articles: $\sum_{word\in article} s(word)$};
    \node [block, left  of=score, node distance=4.5cm]    (cand)   {Candidate articles};
    \node [decision, below of=score, node distance=3.5cm] (decide) {Manually evaluate high scoring articles};

    % Draw edges
    \path [line] (init1)  -- (remove);
    \path [line] (init2)  -- (remove);
    \path [line] (remove) -- (freqs);
    \path [line] (freqs)  -- (lods);
    \path [line] (lods)  -- (score);
    \path [line] (cand)  -- (score);
    \path [line] (score)  -- (decide);
    \path (decide) edge[bend right=90, line width=1mm] node[anchor=init2,right]{no }(init2);
    \path (decide) edge[bend  left=90, line width=1mm] node[anchor=init1,right]{yes}(init1);

%    \path (remove.north) +(0,-2.3) node (clouds) {Build model};
    \path (remove.north) +(-1.5,-2.0) node (clouds) {Build model};

    \begin{pgfonlayer}{background}
        \path (remove.west |- remove.north)+(-0.5,0.3) node (a) {};
        \path (lods.south -| lods.east)+(+0.5,-0.3)    node (b) {};
        \path (clouds.east |- clouds.east)+(+3.5,-7.8)   node (c) {};

        \path[fill=yellow!20,rounded corners, draw=black!50, dashed]
            (a) rectangle (c);           
        \path (remove.north west)+(-0.2,0.2) node (a) {};

    \end{pgfonlayer}

\end{tikzpicture}

\end{document}
